\documentclass{beamer}

% Theme Choice
\usetheme{Madrid}
\usecolortheme{default}

% Packages
\usepackage[utf8]{inputenc}
\usepackage{booktabs}

% Title Page Info
\title[Gramma AI]{Gramma AI: Intelligent Grammar Assistant}
\subtitle{AI-Powered Writing Enhancement}
\author{
Arya Mishra       (2400520100022) //
Abhinav Pal       (2400520100003) //
Ayush Rastogi     (2400520100025) //
Deepanshu Lamba   (2400520100030) //
Hemendra Saraswat (2400520100040)
}
\institute{Department of Computer Science}
\date{March 8, 2026}

\begin{document}

% Slide 1: Title Slide
\begin{frame}
    \titlepage
\end{frame}

% Slide 2: Table of Contents
\begin{frame}{Outline}
    \tableofcontents
\end{frame}

% Slide 3: Introduction
\section{Project Overview}
\begin{frame}{What is Gramma AI?}
    \begin{itemize}
        \item \textbf{Definition:} A deep-learning-based writing assistant.
        \item \textbf{Goal:} Real-time grammatical correction and stylistic suggestions.
        \item \textbf{Key Value:} Bridge the gap between casual and professional writing.
    \end{itemize}
\end{frame}

% Slide 4: Problem Statement
\begin{frame}{The Problem Statement}
    \begin{block}{The Challenge}
        Standard spell-checkers miss context and tone, leading to:
    \end{block}
    \begin{itemize}
        \item Grammatically correct but awkward phrasing.
        \item Inappropriate tone for professional contexts.
        \item High latency in existing cloud-based solutions.
    \end{itemize}
\end{frame}

% Slide 5: System Architecture
\section{System Architecture}
\begin{frame}{Technical Architecture}
    \begin{center}
        
    \end{center}
    \begin{itemize}
        \item \textbf{Frontend:} React.js for seamless user interaction.
        \item \textbf{API Layer:} Python FastAPI for high-performance requests.
        \item \textbf{Model:} Fine-tuned Transformer models (NLP).
    \end{itemize}
\end{frame}

% Slide 6: Core Features
\section{Core Features}
\begin{frame}{Core Features}
    \begin{columns}
        \begin{column}{0.5\textwidth}
            \begin{itemize}
                \item Context-Aware Spellcheck
                \item Sentiment \& Tone Analysis
            \end{itemize}
        \end{column}
        \begin{column}{0.5\textwidth}
            \begin{itemize}
                \item Style Suggestions
                \item Multi-language Support
            \end{itemize}
        \end{column}
    \end{columns}
\end{frame}

% Slide 7: Comparison Table
\begin{frame}{Market Comparison}
    \centering
    \begin{tabular}{lccc}
        \toprule
        \textbf{Feature} & \textbf{Standard} & \textbf{Grammarly} & \textbf{Gramma AI} \\
        \midrule
        Context Check & No & Yes & \textbf{Yes} \\
        Tone Detection & No & Paid & \textbf{Yes} \\
        Open API & No & No & \textbf{Yes} \\
        Offline Support & Yes & No & \textbf{Planned} \\
        \bottomrule
    \end{tabular}
\end{frame}

% Slide 8: Development Workflow
\section{Workflow}
\begin{frame}{Project Workflow (The Linux Way)}
    \begin{enumerate}
        \item \textbf{Data Collection:} Scraping open-source corpora.
        \item \textbf{Training:} Training on Linux-based GPU clusters.
        \item \textbf{Containerization:} Using Docker for consistent deployment.
        \item \textbf{Versioning:} Git-based collaborative development.
    \end{enumerate}
\end{frame}

% Slide 9: Impact
\section{Impact}
\begin{frame}{Social \& Professional Impact}
    \begin{alertblock}{Productivity Boost}
        Reduces proofreading time by approximately 40\%.
    \end{alertblock}
    \begin{itemize}
        \item Empowers non-native English speakers.
        \item Maintains brand consistency in corporate environments.
        \item Enhances academic writing quality.
    \end{itemize}
\end{frame}

% Slide 10: Future Scope
\begin{frame}{Future Scope}
    \begin{itemize}
        \item Integration with IDEs (VS Code, IntelliJ).
        \item Predictive text generation based on user history.
        \item Real-time voice-to-text grammar correction.
    \end{itemize}
\end{frame}

% Slide 11: Conclusion
\begin{frame}{Conclusion}
    \centering
    \Huge Thank You! \\
    \vspace{10pt}
    \normalsize \textbf{Questions?}
\end{frame}

\end{document}

# Thank You!

**Gramma AI – Elevating Every Word.**
